Title Goes Here

### 2020-03-26 analysis/paper/paper.Rmd
push before updating my r

#distance between landmarks

@@

# Maximum length of stem:

@@

#gather ML and BL of all artifacts
ML = c()
BL = c()
for (i in 1:length(files)) {
  filename <- paste(datadir, files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
}

#list of ML and BL
df <- data.frame(ML, BL, files)

#Making a plot for ML and BL
plot(df$ML, df$BL)

>>>>

#distance between landmarks(euclidean)

@@

# Maximum length of stem: SL, distance between landmark 9-7 or 4-7 (y axis)
sl_dist <- function(landmarks) {
  s1 = vertical_dist(landmarks, 9, 7)
  s2 = vertical_dist(landmarks, 4, 7)
  max(s1, s2)
}

SL <- sl_dist

# Mid width: MW, distance between landmark 2-11
MW <- landmark_dist(landmarks, 2, 11)

# Maximum width of Tang: TW, distance between landmark 3-10
TW <- landmark_dist(landmarks, 3, 10)

# Stem width: SW, distance between landmark 5-8
SW <- landmark_dist(landmarks, 5, 8)

@@

#gather ML and BL of all artifacts
ML = c()
BL = c()
TL = c()
SL = c()
MW = c()
TW = c()
SW = c()
for (i in 1:length(files)) {
  filename <- paste(datadir, files[i], sep = "")
  print(filename)
  landmarks <- read.tps(filename)
  ML <- c(ML, landmark_dist(landmarks, 1, 7))
  BL <- c(BL, bl_dist(landmarks))
  TL <- c(TL, tl_dist(landmarks))
  SL <- c(SL, sl_dist(landmarks))
  MW <- c(MW, landmark_dist(landmarks, 2, 11))
  TW <- c(TW, landmark_dist(landmarks, 3, 10))
  SW <- c(SW, landmark_dist(landmarks, 5, 8))
}

#list of all attributes
df <- data.frame(ML, BL, TL, SL, MW, TW, SW, files)
